power_analyses

### 2024-02-07 manuscript.Rmd
- Collected and analzed data - Wrote results and discussion section

abstract          : "Privacy is defined as a voluntary withdrawal from society. While everyone needs some degree of privacy, we currently know little about people’s privacy needs. In this study, we explore the relations between the need for privacy and personality. Personality will be operationalized using the HEXACO personality inventory. Need for privacy will be measured in relation to social, psychological, and physical privacy from other individuals (horizontal privacy); need for privacy from government agencies and companies (vertical privacy); as well as need for informational privacy, anonymity, and general privacy (both horizontal and vertical privacy). A sample of 1,576 respondents representative of the U.S. in terms of age, gender, and ethnicity will be collected. The correlations between privacy, personality, and sociodemographics will be analyzed using structural equation modeling."
keywords          : "Privacy, need for privacy, personality, HEXACO"

@@

header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
  - \note{\clearpage}
  - \usepackage{float}
---

@@

```{r setup, include=F}
# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
packages <- c("devtools", "english", "ggplot2", "kableExtra", "lavaan", 
              "magrittr", "papaja", "semPlot", "simsem", "td", "tidyverse")
lapply(packages, library, character.only = TRUE)
load("data/workspace.RData")

@@

In predicting the need for privacy, we will primarily focus on the facets, because it is unlikely that the very specific need for privacy dimensions will relate closely to more general personality factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008]. 
And for reasons of scope, below we cannot discuss all four facets for all six factors. Instead, we focus on those we consider most relevant. However, all we be analyzed empirically.

@@

<!-- To understand why people desire privacy, we can also adopt an evolutionary perspective. -->
Privacy also has strong evolutionary roots [@acquistiHowPrivacyMay2022].
Confronted with a threat---for example, the prototypical a tiger---people are inclined to withdraw.
In the presences of opportunities---for example, the unexpected sharing of resources---people open up and approach one another.
Transferred to privacy, we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.
Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].
Privacy also affords the opportunity to hide less socially desirable aspects of the self from others, which may bestow evolutionary advantages in terms of sexual selection or other social benefits and opportunities. 
Indeed, the need for privacy may have evolved precisely because it offers such advantages.

@@

Empirical studies have linked privacy to increased cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
@coveySelfmonitoringSurveillanceIncentive1989 asked students to solve an impossible maze. 
In the surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. 
In the privacy condition, the experimenter could not see the students. 
Results showed greater cheating among students in the privacy condition, suggesting that in situations with more privacy people are less honest. 
While this shows a connection between privacy and dishonesty, other studies more directly support the notion that a desire for privacy is related to increased dishonesty.
In a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48).
People who needed more privacy were also less authentic in their personal relationships (_r_ = -.28). 
<!-- Together, these studies suggest the possibility that lack of honesty may relate to an increased need for privacy, especially when it comes to government surveillance.    -->

@@

<!-- Need for privacy might relate to a person’s level of emotionality.  -->
Emotionality is captured by the facets fearfulness, anxiety, dependence, and sentimentality.
People who are anxious may be more likely to view social interactions as risky or threatening [especially with strangers or weak ties, @granovetterStrengthWeakTies1973].
Anxious people might hence desire more privacy. 
People who are more concerned about their privacy (in other words, more anxious about privacy) may be more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content to minimize risk [@dienlinExtendedPrivacyCalculus2016].
On the other hand, the opposite may also be true: 
People who are more anxious in general may desire less privacy from others (especially their strong ties), as a means to cope better with their daily challenges or to seek social approval to either verify or dispel their social anxiety.

@@

Conscientiousness consists of the facets organization, diligence, perfectionism, and prudence.
Arguably, all facets are about being in control, about reducing relevant risks and future costs.
Because control is a central part of privacy [@westinPrivacyFreedom1967], people who avoid risks, who deliberate, and who plan ahead carefully, might prefer to have more privacy because it affords them greater control. 
Especially if others are considered a threat, being risk averse might increase the desire for more horizontal privacy. 
Similarly, if government agencies or private companies are considered a threat, risk averse people might have a stronger desire for vertical privacy. 
In either case, the most cautious strategy to minimize risks of information disclosure would be to keep as much information as possible private. 
Empirical studies have found that people with a stronger control motive require slightly more seclusion (_r_ = .12) and anonymity (_r_ = .15) [@hosmanRelationshipsNeedPrivacy1991].
People who considered their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018]. 
Moreover, conscientious people are more concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
<!-- But as discussed above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, so that the government is able to avert potential threats.  -->
<!-- In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study. -->

@@

This section describes how we determine the sample size, data exclusions, the analyses, and all measures in the study.
The Study will be conducted as an online questionnaire, programmed with Qualtrics.
A preview of the survey can be found [here](https://compcommlab.eu.qualtrics.com/jfe/preview/previewId/5c6193c9-12a4-424f-9808-a7c6e74247c1/SV_9ppRmr32VrmeAnA?Q_CHL=preview&Q_SurveyVersionID=current).

@@

This study builds on a prior project in which we analyzed the same research question [@dienlinWhoNeedsPrivacy2019]. 
This study was already submitted to Collabra, but rejected.
The main reasons were that the sample was too small, that not one coherent personality inventory was used, that most privacy measures were designed ad-hoc, and that the inferences were too ambitious. 
We hence decided to treat our prior project as a pilot study and to address the criticism by conducting a new study.
In this new study, we redevelop our study design, we collect a larger sample, implement the HEXACO inventory together with established need for privacy measures, and overall adopt a more exploratory perspective. 
Being our central construct of interest, we also develop a small number of new items to have a more comprehensive measure of need for privacy.

@@

Participants will be collected from the professional online survey panel Prolific. 
The sample will be representative of the US in terms of age, gender, and ethnicity. 
The study received IRB approval from the University of Vienna (#20210805_067).
We calculated that participation will take approximately 15 minutes. 
We will pay participants \$2.00 for participation, which equals an hourly wage of \$8.00.

To determine sample size, we ran a priori power analyses using the R package _simsem_ [@R-simsem].
We based our power analysis on a smallest effect size of interest (SESOI; see also below).
We only considered effects at least as great as _r_ = .10 as sufficiently relevant to support an effect's existence [@cohenPowerPrimer1992]. <!-- Note that the final analyses will be conducted using structural equation modeling (SEM), for which exact power analyses are difficult to obtain.  -->
<!-- We therefore conducted preliminary power analyses using two-sided bivariate correlations.  -->
To estimate power, we simulated data."
We set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10.
We, furthermore, set the latent factor loadings to be $\lambda$ = .85 (the SESOI)
<!-- Hence, the following power analyses are not exact but rather a rough guide to get a better idea of the required minimum sample size. -->
<!-- Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%). -->
Adopting an exploratory perspective, and not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].
Because balanced alpha and beta errors of 5% are outside of our budget, we opted for balanced alpha and beta errors of 10%.
A power analysis with an alpha and beta error of 10% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
To account for potential attrition (see below), we will oversample by five percent, leading to a final sample size of N = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
We obtained sufficient funding to collect a sample of this size.
<!-- Hence, we will use two inference criteria: Effects need to show a _p_-value of below _p_ = 10% and an effect size of at least _r_ = .10.  -->

@@

We will individually check answers for response patterns such as straight-lining or missing of inverted items.
We will conservatively remove participants with clear response patterns.
We will automatically exclude participants who miss the two attention checks we will implement.
Participants who miss one attention check will be checked individually regarding response patterns.
We will remove participants below the minimum participation age of 18 years.
We will remove respondents with unrealistically fast responses (three standard deviations below the median response time). 
<!-- We will exclude respondents if they answer fewer than 50% of all questions.  -->

Missing responses will be imputed using multiple imputation with predictive mean matching (ten datasets, five iterations, using variables that correlate at least with _r_ = .10). 
The analyses will be run with all ten datasets, and the pooled results will be reported.

## Planned Analyses

<!-- We will test items for potential ceiling and floor effects.  -->
<!-- If means are below 1.5 or above 6.5, these items will be excluded. -->
The factorial validity of the measures and the relations will be tested using structural equation modeling. 
If Mardia’s test shows that the assumption of multivariate normality is violated, we will use the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator. 
We will test each scale in a confirmatory factor analysis. 
To assess model fit, we will use more liberal fit criteria to avoid overfitting (CFI > .90, TLI > .90, RMSEA < .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
In cases of misfit, we will conservatively alter models using an a priori defined analysis pipeline (see online supplementary material).
As a “reality check,” we will test items for potential ceiling and floor effects. If means are below 1.5 or above 6.5, these items will be excluded.

We want to find out _who_ needs privacy, and not so much _what causes_ the need for privacy.
Hence, to answer our research question, in a joint model combining all variables (including sociodemographic variables) we will analyze the variables' bivariate relations. 
To predict the need for privacy, we will first use the six personality factors.
Afterward, we will predict privacy using the more specific facets. 
To get a first idea of the variables' potential causal relations, we will also run a multiple structural regression model.
<!-- We will also test which individual items best predict need for privacy. -->

We will use two measures as inference criteria: statistical significance and effect size. 
Regarding statistical significance, we will use an alpha value of 10%.
Regarding effect size, we will define a SESOI of _r_ = .10, and thereby a null-region ranging from -.10 to .10.
As proposed by @dienesUsingBayesGet2014, we will consider effects to be meaningful if the confidence interval falls outside of the null region (e.g., .15 to .25 or -.15 to -.25).
We will consider effects irrelevant if the confidence interval falls completely within the null region (e.g., .02 to .08).
And we will suspend judgement if the confidence intervals partially include the null region (e.g., .05 to .15).

Fully latent SEMs seldom work instantly, often requiring modifications to achieve satisfactory model fit.
Although we explicate our analysis pipeline, there still remain several researcher degrees of freedom. 
We decided to use fully latent SEMs because we consider it superior to regular analyses such as correlation or regression using manifest variables [@klinePrinciplesPracticeStructural2016]. 
Combining several items into latent factors helps reduce noise and thereby the beta error. 
To provide context, in the online supplementary material (OSM) we will also share the results of alternative analyses, such as correlations of average scores.

We anticipate to finish the project three months after our registration was accepted.

@@

All items will be answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
A list of all the items that we will use are reported in the online supplementary material. 
The personality and privacy items will be presented in random order, and the sociodemographic questions will be asked at the end.
We will later report also the results of the CFAs/EFAs, as well as item statistics and their distribution plots.

@@

Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2023; @marshallDimensionsPrivacyPreferences1974], we are not aware of one encompassing, comprehensive, and up-to-date scale. 
Hence, we use both existing scales and self-developed items, some of which were tested in our pilot study. 
Ad-hoc scales were or will be (preliminarily) validated using the following procedure:
We (a) collected qualitative feedback from three different privacy experts;[^experts]
(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 to test (and adapt) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2023, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; (d) all items will be analyzed in confirmatory factor analyses as outlined above.

@@

Overall, we will collect 32 items measuring need for privacy, with eight subdimensions that all consist of four items each. 
Three subdimensions capture horizontal privacy---namely _psychological_, _social_, and _physical_ privacy from other individuals. 
Psychological and physical privacy were adopted from @frenerDevelopmentValidationNeed2023.
Because @frenerDevelopmentValidationNeed2023 could not successfully operationalize the dimension of social privacy, building on @burgoonPrivacyCommunication1982 we self-designed a new social privacy dimension, which in the prestudy showed satisfactory fit. 
Two subdimensions measure vertical privacy.
The first subdimension is _government surveillance_, which represents the extent to which people want the government to abstain from collecting information about them. 
The scale was pretested and showed good factorial validity. 
The second subdimension is need for privacy from _companies_, which we will measure using four new self-designed items.
Finally, three subdimensions capture general privacy. 
The first subdimension is _informational_ privacy, with items adopted from @frenerDevelopmentValidationNeed2023.
The second subdimension is _anonymity_, which captures the extent to which people feel the need to avoid identification in general.
The scale was pretested and showed good factorial validity; one new item was designed for this study.
Third, we will also collect a new self-developed measure of _general_ need for privacy.

@@

Personality will be measured using the HEXACO personality inventory. 
The inventory consists of six factors with four facets each, including the additional meta scale of "altruism".

@@

To visualize how results might look like, we have simulated some random data. Please note that these results are completely random and do not make sense from a theoretical perspective. 
When calculating the multiple regressions, the models did not converge, which is why several estimates could not be computed (see below).

In Table \@ref(tab:tab-ses), we report how sociodemographics predict need for privacy.

```{r tab-ses, cache=F, warning=F, message=F, prompt=F}
# tab_ses %<>% set_names(c("Sociodemographics", vars_pri_txt_brk))
tab_ses %<>% set_names(c("Sociodemographics", vars_pri_txt_abr))

apa_table(tab_ses,
          # stub_indents = list("Sociodemographics" = c(1:6)),
          col_spanners = list(`Need for privacy` = c(2, 9)),
          caption = "Predicting the need for privacy dimensions using sociodemographic variables.",
          font_size = "small",
          escape = FALSE
          )
```

In Table \@ref(tab:tab-dim), we report how personality factors predict need for privacy.

```{r tab-dim, cache=F, warning=F, message=F, prompt=F}
tab_dim %<>% set_names(c("Personality factors", vars_pri_txt_abr))

apa_table(tab_dim,
          # stub_indents = list("Sociodemographics" = c(1:6)),
          col_spanners = list(`Need for privacy` = c(2, 9)),
          caption = "Predicting the need for privacy dimensions using personality factors.",
          font_size = "small",
          escape = FALSE
          )
```

In Table \@ref(tab:tab-fac), we report how personality facets predict need for privacy.

```{r tab-fac, cache=F, warning=F, message=F, prompt=F}
tab_fac %<>% set_names(c("Personality facets", vars_pri_txt_abr))

apa_table(tab_fac,
          stub_indents = list(
            "Honesty humility" = c(1:4),
            "Emotionality" = c(5:8),
            "Extraversion" = c(9:12),
            "Agreableness" = c(13:16),
            "Conscientiousness" = c(17:20),
            "Openness to experiences" = c(21:24)
            ),
          col_spanners = list(`Need for privacy` = c(2, 9)),
          caption = "Predicting the need for privacy dimensions using personality facets.",
          font_size = "scriptsize",
          escape = FALSE
          )
```

In Figure \@ref(fig:fig-reg), you can find how each personality factor---while holding constant all other personality factors and sociodemographics---predicts need for privacy.

```{r fig-reg, fig.cap="Results of multiple regressions, in which we predict all dimensions of need for privacy using all personality facets and sociodemgraphic factors simultaneously.", out.width = "\\textwidth", cache=F, warning=F, message=F, prompt=F, fig.pos='H'}
# fig_desc
knitr::include_graphics("figures/fig_reg.png")
```

>>>>

abstract          : "Privacy is defined as a voluntary withdrawal from society. While everyone needs some degree of privacy, we currently know little about who needs how much. In this study, we explored the relations between the need for privacy and personality. Personality was operationalized using the HEXACO personality inventory. Need for privacy was measured in relation to social, psychological, and physical privacy from other individuals (horizontal privacy); need for privacy from government agencies and companies (vertical privacy); as well as need for informational privacy, anonymity, and general privacy (both horizontal and vertical privacy). A sample of 1,576 respondents representative of the U.S. in terms of age, gender, and ethnicity was collected. The results showed several substantial relationships: More extraverted people needed substantially more privacy. People less honest, less fair, and less altruistic needed more privacy, lending some support to the nothing to hide-argument. More conservative respondents needed more privacy from the government."
keywords          : "Privacy, need for privacy, personality, HEXACO"

@@

header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
  - \note{\clearpage}
  - \usepackage{float}
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
---

@@

```{r setup, include=F}
# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
library(devtools)
library(english)
library(ggplot2)
library(kableExtra)
library(lavaan)
library(magrittr)
library(naniar)
library(papaja)
library(semPlot)
library(simsem)
library(td)
library(tidyverse)

load("data/workspace_2.RData")

source("custom_functions.R")

@@

In predicting the need for privacy, we will primarily focus on the facets, because it is unlikely that the very specific need for privacy dimensions will relate closely to more general personality factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008]. 
And for reasons of scope, below we cannot discuss all four facets for all six factors. Instead, we focus on those we consider most relevant. However, all will be analyzed empirically.

@@

<!-- To understand why people desire privacy, we can also adopt an evolutionary perspective. -->
Privacy has strong evolutionary roots [@acquistiHowPrivacyMay2022].
Confronted with a threat---for example, the prototypical tiger---people are inclined to withdraw.
In the presences of opportunities---for example, the unexpected sharing of resources---people open up and approach one another.
Transferred to privacy, we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.
Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].
Privacy also affords the opportunity to hide less socially desirable aspects of the self from others, which may bestow evolutionary advantages in terms of sexual selection or other social benefits and opportunities. 
Indeed, the need for privacy may have evolved precisely because it offers such advantages.

@@

Empirical studies have linked privacy to increased cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
@coveySelfmonitoringSurveillanceIncentive1989 asked students to solve an impossible maze. 
In the surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. 
In the privacy condition, the experimenter could not see the students. 
Results showed greater cheating among students in the privacy condition, suggesting that in situations with more privacy people are less honest. 
<!-- While this shows a connection between privacy and dishonesty, other studies more directly support the notion that a desire for privacy is related to increased dishonesty. -->
In a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48).
People who needed more privacy were also less authentic in their personal relationships (_r_ = -.28). 
<!-- Together, these studies suggest the possibility that lack of honesty may relate to an increased need for privacy, especially when it comes to government surveillance.    -->

@@

<!-- Need for privacy might relate to a person’s level of emotionality.  -->
Emotionality is captured by the facets fearfulness, anxiety, dependence, and sentimentality.
People who are anxious may be more likely to view social interactions as risky or threatening [especially with strangers or weak ties, @granovetterStrengthWeakTies1973].
Anxious people might hence desire more privacy. 
People who are more concerned about their privacy (in other words, more anxious about privacy) are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content to minimize risk [@dienlinExtendedPrivacyCalculus2016].
On the other hand, the opposite may also be true: 
People who are more anxious in general may desire less privacy from others (especially their strong ties), as a means to cope better with their daily challenges or to seek social approval to either verify or dispel their social anxiety.

@@

Conscientiousness consists of the facets organization, diligence, perfectionism, and prudence.
Arguably, all facets are about being in control, about reducing relevant risks and future costs.
Because control is a central part of privacy [@westinPrivacyFreedom1967], people who avoid risks, who deliberate, and who plan ahead carefully might prefer to have more privacy because it affords them greater control. 
Especially if others are considered a threat, being risk averse might increase the desire for more horizontal privacy. 
Similarly, if government agencies or private companies are considered a threat, risk averse people might have a stronger desire for vertical privacy. 
In either case, the most cautious strategy to minimize risks of information disclosure would be to keep as much information as possible private. 
Empirical studies have found that people with a stronger control motive require slightly more seclusion (_r_ = .12) and anonymity (_r_ = .15) [@hosmanRelationshipsNeedPrivacy1991].
People who considered their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018]. 
Moreover, conscientious people are more concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
<!-- But as discussed above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, so that the government is able to avert potential threats.  -->
<!-- In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study. -->

@@

This section describes how we determined the sample size, data exclusions, the analyses, and all measures in the study.
The Study was conducted as an online questionnaire, programmed with Qualtrics.
The survey can be found in the [online supplementary material](https://osf.io/e47yw/files/osfstorage/65c363e69b32ca0b4397f002).

@@

This study builds on a prior project in which we analyzed the same research question [@dienlinWhoNeedsPrivacy2019]. 
This study was already submitted to Collabra but rejected.
The main reasons were that the sample was too small, that not one coherent personality inventory was used, that most privacy measures were designed ad-hoc, and that the inferences were too ambitious. 
We hence decided to treat our prior project as a pilot study and to address the criticism by conducting a new study.
In this new study, we redeveloped our study design, collected a larger sample, implemented the HEXACO inventory together with established need for privacy measures, and overall adopted a more exploratory perspective. 
Being our central construct of interest, we also developed a small number of new items to have a more comprehensive measure of need for privacy.

@@

Participants were collected from the professional online survey panel Prolific. 
The sample was representative of the US in terms of age, gender, and ethnicity. 
The study received IRB approval from the University of Vienna (#20210805_067).
Participation took on average `r round(time_m, 0) ` minutes. 
We paid participants \$2.00 for participation, which equals an hourly wage of \$8.00.

To determine sample size, we ran a priori power analyses using the R package _simsem_ [@R-simsem].
We based our power analysis on a smallest effect size of interest (SESOI; see below).
We only considered effects at least as great as _r_ = .10 as sufficiently relevant to support an effect's existence [@cohenPowerPrimer1992]. <!-- Note that the final analyses will be conducted using structural equation modeling (SEM), for which exact power analyses are difficult to obtain.  -->
<!-- We therefore conducted preliminary power analyses using two-sided bivariate correlations.  -->
To estimate power, we simulated data.
We set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10 (the SESOI).
We, furthermore, set the latent factor loadings to be $\lambda$ = .85.
<!-- Hence, the following power analyses are not exact but rather a rough guide to get a better idea of the required minimum sample size. -->
<!-- Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%). -->
Adopting an exploratory perspective, and not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].
Because balanced alpha and beta errors of 5% were outside of our budget, we opted for balanced alpha and beta errors of 10%.
A power analysis with an alpha and beta error of 10% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
To account for potential attrition (see below), we oversampled by five percent, leading to a planned sample size of N = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
<!-- Hence, we will use two inference criteria: Effects need to show a _p_-value of below _p_ = 10% and an effect size of at least _r_ = .10.  -->
In the end, `r n_finished` respondents successfully finished our study, slightly exceeding our plans.

@@

We individually checked answers for response patterns such as straight-lining or missing of inverted items.
We planned to conservatively remove participants with clear response patterns.
However, as no clear patterns emerged we maintained all participants.
We automatically excluded participants who missed the two attention checks we implemented.
Overall, 30 participants were filtered out automatically by Prolific, not counting toward our quota.
Participants who missed one attention check were checked individually regarding response patterns.
Again, no clear patterns emerged.
We planned to remove participants below the minimum participation age of 18 years.
As no minors took part in our study we did not exclude any participant for this reason.
We planned to remove respondents with unrealistically fast responses (three standard deviations below the median response time). 
The median response time was `r round(time_med / 60, 0)` minutes and the standard deviation `r round(time_sd / 60, 0)` minutes. 
Hence, three SDs below median was `r round(time_crit_init / 60, 0)` minutes, hence not informative. 
Instead, we decided to remove respondents who took less than five minutes answering the questionnaire, which we considered unreasonably fast.
We removed `r n_speeding %>% english::english()` participants for this reason.
<!-- We will exclude respondents if they answer fewer than 50% of all questions.  -->

We planned to impute missing responses using multiple imputation with predictive mean matching (ten datasets, five iterations, using variables that correlate at least with _r_ = .10). 
However, as there were only `r n_miss(d)` answers missing in total (`r round(prop_miss(d) * 100, 3)` percent), we decided not to impute any data.
The final sample size was _N_ = `r nrow(d)`.

## Analyses

<!-- We will test items for potential ceiling and floor effects.  -->
<!-- If means are below 1.5 or above 6.5, these items will be excluded. -->
The factorial validity of the measures and the relations were tested using structural equation modeling. 
If Mardia’s test showed that the assumption of multivariate normality was violated, we used the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator (or, in the few cases of missing data MLR plus FIML estimation).
We tested each scale in a confirmatory factor analysis. 
To assess model fit, we used more liberal fit criteria to avoid overfitting (CFI > .90, TLI > .90, RMSEA < .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
In cases of misfit, we conservatively altered models using an a priori defined analysis pipeline (see online supplementary material).
As a “reality check,” we tested items for potential ceiling and floor effects. 
If means were below 1.5 or above 6.5, we preregistered to exclude these items.
However, as no item was outside these threshold, no items were excluded.

We wanted to find out _who_ needs privacy, and not so much _what causes_ the need for privacy.
Hence, to answer our research question, in a joint model combining all variables (including sociodemographic variables) we analyzed the variables' bivariate relations. 
To predict the need for privacy, we first used the six personality factors.
Afterward, we predicted privacy using the more specific facets. 
To get a first idea of the variables' potential causal relations, we also planned to run latent structural regression models.
However, because model fit was not acceptable we analyzed the potential effects in a multiple regression using the mean values of the observed scores. 
<!-- We will also test which individual items best predict need for privacy. -->

We used two measures as inference criteria: statistical significance and effect size. 
Regarding statistical significance, we used an alpha value of 10%.
Regarding effect size, we defined a SESOI of _r_ = .10, and thereby a null-region ranging from -.10 to .10.
As proposed by @dienesUsingBayesGet2014, we considered effects to be meaningful if the confidence interval fell outside of the null region (e.g., .15 to .25 or -.15 to -.25).
We considered effects irrelevant if the confidence interval fell completely within the null region (e.g., .02 to .08).
And we suspended judgement if the confidence intervals partially included the null region (e.g., .05 to .15).

Fully latent SEMs seldom work instantly, often requiring modifications to achieve satisfactory model fit.
Although we explicated our analysis pipeline, there still remained several researcher degrees of freedom. 
We planned to use fully latent SEM because we consider it superior to regular analyses such as correlation or regression using manifest variables [@klinePrinciplesPracticeStructural2016]. 
However, as several of the scales showed suboptimal fit, we decided to report the more conservative correlations of average scores.
In the online supplementary material (OSM) we also share the results of alternative analyses, such as fully latent SEMs.

@@

All items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
A list of all the items that we were used are reported in the online supplementary material. 
The personality and privacy items were presented in random order, and the sociodemographic questions were asked at the end.
Online we also report all item statistics and their distribution plots.

@@

Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2023; @marshallDimensionsPrivacyPreferences1974], we are not aware of one encompassing, comprehensive, and up-to-date scale. 
Hence, we used both existing scales and self-developed items, some of which were tested in our pilot study. 
Ad-hoc scales were validated using the following procedure:
We (a) collected qualitative feedback from three different privacy experts;[^experts]
(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 to test (and adapt) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2023, assessed convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; (d) analyzed all items in confirmatory factor analyses as outlined above.

@@

Overall, we collected 32 items measuring need for privacy, with eight subdimensions that all consisted of four items each. 
Three subdimensions captured horizontal privacy---namely _psychological_, _social_, and _physical_ privacy from other individuals. 
Psychological and physical privacy were adopted from @frenerDevelopmentValidationNeed2023.
Because @frenerDevelopmentValidationNeed2023 could not successfully operationalize the dimension of social privacy, building on @burgoonPrivacyCommunication1982 we self-designed a new social privacy dimension, which in the prestudy showed satisfactory fit. 
Two subdimensions measured vertical privacy.
The first subdimension was _government surveillance_, which represents the extent to which people want the government to abstain from collecting information about them. 
The scale was pretested and showed good factorial validity. 
The second subdimension was need for privacy from _companies_, which we measured using four new self-designed items.
Finally, three subdimensions captured general privacy. 
The first subdimension was _informational_ privacy, with items adopted from @frenerDevelopmentValidationNeed2023.
The second subdimension was _anonymity_, which captured the extent to which people feel the need to avoid identification in general.
The scale was pretested and showed good factorial validity; one new item was designed for this study.
Third, we also collected a new self-developed measure of _general_ need for privacy.

@@

Personality were measured using the HEXACO personality inventory. 
The inventory consists of six factors with four facets each, including the additional meta scale of "altruism".

@@

We first tested the factorial validity of all measures.
When analyzed individually, most measures showed satisfactory model fit, not requiring any changes.
Some measures showed satisfactory model fit after small adaptions, such as allowing items to covary.
In terms of reliability, most measures showed satisfactory results.
However, some measures such as altruism, unconventionality, or anonymity showed insufficient reliability.
Instead of strongly adapting measures, we decided to maintain the initial factor structure and did not delete any items or did not introduce substantial changes to the factors.
For an overview of all measures, their descriptives and factorial validity, see Table \@ref(tab:tab-des).
Although individually most of the measures showed good fit, when analyzed together fit decreased substantially, below acceptable levels. 
As a result, we conservatively decided to analyze our data using the variables' observed mean scores.

```{r tab-des, cache=F, warning=F, message=F, prompt=F}
apa_table(
  tab_des, 
  stub_indents = list(
    "Personality" = c(1:31),
    "Need for Privacy" = c(32:39)
    ),
  align = c("l", rep("r", 8)),
  caption = "Factorial validity of all measures.",
  font_size = "small",
  escape = FALSE
  )
```

The need for privacy measures showed good convergent validity.
If respondents reported higher needs for privacy they were also more concerned about their privacy, with coefficients ranging from _r_ = .21 to _r_ = .73.
The only exception was the relation between privacy concerns and the need for social privacy, which was very small (_r_ = .09).
Similarly, if respondents reported higher needs of privacy they also engaged in more privacy behaviors, with coefficients ranging from _r_ = .20 to _r_ = .71
The only exception was the relation between privacy behavior and the need for social privacy, which was virtually nonexistent (_r_ = .01), and the need for physical privacy, which was very small (_r_ = .09).
See online supplementary material for all results.

People who reported being less honest and humble needed more anonymity (`r get_res("Honesty humility", "Anonymity")`).
Looking at facets, more anonymity was needed by people who reported being less fair (`r get_res("Fairness", "Anonymity")`), less modest (`r get_res("Modesty", "Anonymity")`), and less altruistic (`r get_res("Altruism", "Anonymity")`).
However, less sincere people needed less privacy from companies (`r get_res("Sincerity", "Companies")`) and less privacy in general (`r get_res("Sincerity", "General")`).
Effects were small or small-to-medium sized.

Several relations between emotionality and need for privacy were found.
More emotional people needed less psychological privacy (`r get_res("Emotionality", "Psychological")`), less privacy from the government (`r get_res("Emotionality", "Government")`), less anonymity (`r get_res("Emotionality", "Anonymity")`)---but also more physical privacy (`r get_res("Emotionality", "Physical")`).
More anxious respondents needed substantially more social (`r get_res("Anxiety", "Social")`) and physical privacy (`r get_res("Anxiety", "Physical")`).
Similarly, more fearful respondents needed more social (`r get_res("Fearfulness", "Social")`) and physical privacy (`r get_res("Fearfulness", "Physical")`).
More dependent participants generally needed less privacy, including less psychological (`r get_res("Dependence", "Psychological")`) and social privacy (`r get_res("Dependence", "Social")`), less privacy from the government (`r get_res("Dependence", "Government")`), and less informational (`r get_res("Dependence", "Informational")`) and general privacy (`r get_res("Dependence", "General")`).
A similar picture for more sentimental participants emerged, who needed less psychological (`r get_res("Sentimentality", "Psychological")`) and social privacy (`r get_res("Sentimentality", "Social")`) and less anonymity (`r get_res("Sentimentality", "Anonymity")`).
